Indexes measures for oak decline severity using phenotypic descriptors

### 2019-07-03 outline/outline.Rmd
alterations to outline

---
title: "Indexes for measuring acute and chronic oak decline severity using phenotypic descriptors"
output: word_document
---

@@

- Suitability of collected phenotypic descriptors for describing decline status
- Decline index calculation
- Comparison of indexes with manually assigned decline status labels
- Index thresholds for category definitions (healthy, declining, severe decline etc.)

@@

**Figure 1:** Site differences MDS plot and feature importance (top ranked trends)

**Figure 2:** Example of site correction effect on a descriptor

**Figure 3:** Decline index scales (graphical representations of the indexes)

**Figure 4:** Decline index descriptor contributions and trends of top ranked

>>>>

---
title: "Indexes measures for oak decline severity using phenotypic descriptors"
output: word_document
---

@@

- Suitability of collected phenotypic descriptors for describing decline status
- Decline index calculation
- Comparison of indexes with manually assigned decline status labels
- Top ranked descriptor index response surfaces
- Index thresholds for category definitions (healthy, declining, severe decline etc.)

@@

**Figure 1:** 
    - a) Site differences MDS plot
    - b) Site difference feature importance
    - c) Example of site correction effect on a descriptor

**Figure 2:** Decline index scales (graphical representations of the indexes)

**Figure 3:** Decline index descriptor contributions

**Figure 4:** Top ranked descriptor response surfaces
